GRHL2

### 2018-02-09 ChIP-seq_GRHL2/Manuscript_Figures.Rmd
Add Suppl. Figure 92

>>>>

###  GRHL2 overlap with Gro-SEQ data is reproducible between studies

```{r GroSeq2, fig.cap="Analysis of GRHL2 sites of Gro-Seq data from  GSE43836 and GSE45822 both showed that E2 responsive GRHL2 resonsive sites are transcriptionally responsive to E2." }
GSE43836<-read.csv("txt/averaged_GSE43836.csv")

colnames(GSE43836)[1]<-"Distance from Center/bp"

par(mfrow=c(2,2))

plot(GSE43836[1:2],ylim=c(0,6),type="n", lwd=2, ylab="Read Depth", main="All GRHL2 Sites [GSE43836]")
lines(GSE43836[c(1,2)], lwd=2, col="lightblue")
lines(GSE43836[c(1,3)], lwd=2,  col="pink")
lines(GSE43836[c(1,4)], lwd=2,  col="deeppink")
legend("topright", legend=c("0 min", "45 min", "90 min"),
       col=c("lightblue","pink","deeppink"),pch=20, cex=0.5, horiz = TRUE)

plot(GSE43836[1:2],ylim=c(0,6),type="n", lwd=2, ylab="Read Depth", main="All GRHL2 Sites [GSE43836]")
lines(GSE43836[c(1,5)], lwd=2, col="lightblue")
lines(GSE43836[c(1,6)], lwd=2,  col="pink")
lines(GSE43836[c(1,7)], lwd=2,  col="deeppink")
legend("topright", legend=c("0 min", "45 min", "90 min"),
       col=c("lightblue","pink","deeppink"),pch=20, cex=0.5,horiz = TRUE)

GSE45822<-read.csv("txt/averaged_GSE45822.csv")

colnames(GSE45822)[1]<-"Distance from Center/bp"

plot(GSE45822[1:2],ylim=c(0,6),type="n", lwd=2, ylab="Read Depth", main="All GRHL2 Sites [GSE45822]")
lines(GSE45822[c(1,3)], lwd=2, col="lightblue")
lines(GSE45822[c(1,2)], lwd=2,  col="deeppink")
legend("topright", legend=c("Veh", "E2"),
       col=c("lightblue","deeppink"),pch=20, cex=0.5,horiz = TRUE)

plot(GSE45822[1:2],ylim=c(0,6),type="n", lwd=2, ylab="Read Depth", main="All GRHL2 Sites [GSE45822]")
lines(GSE45822[c(1,5)], lwd=2, col="lightblue")
lines(GSE45822[c(1,4)], lwd=2,  col="deeppink")
legend("topright", legend=c("Veh", "E2"),
       col=c("lightblue","deeppink"),pch=20, cex=0.5,horiz = TRUE)
